Stan Introduction

### 2019-08-16 Code/Stan-introduction.Rmd
Rmarkdown outputed to a Github Doc

---
title: "Stan Introduction"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

@@

```{r}
mymodeldata = list(
  N = 100,
  Y = rnorm(N, 1.6, 0.2)
)
fit = stan(
  file = here::here("my_stan_model.stan"),
  data = mymodeldata,
  seed = 42
)
```

>>>>

---
title: "Stan Introduction"
output: github_document
---

@@

```{r}
mymodeldata = list(
  N = 100,
  Y = rnorm(N, 1.6, 0.2)
)
fit = stan(
  file = here::here("Code", "my_stan_model.stan"),
  data = mymodeldata,
  seed = 42
)
```
